Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-01-10 paper/paper.tex
More words
Notation, etc

?? Heuristics

@@

Our experiments were performed on systems with Intel Xeon E5-4650 v2 (Q1'14) CPUs and 768GBytes RAM
(although this much RAM was not needed), running Scientific Linux release 6.7.   ?? Software
versions. Clasp 3.1.3, Gurobi 6.0.5, Glasgow, LAD version 2, VFLib. Software was compiled using GCC
4.9.

@@

By repeating the argument for locating the non-induced phase transition and additionally considering
non-edges, we get an expected number of solutions of \[ \langle Sol \rangle = t^{\underline{p}}
\cdot {d_t}^{d_p \cdot \binom{p}{2}} \cdot {d_{\overline{t}}}^{d_{\overline{p}} \cdot \binom{p}{2}}
\textnormal{,} \] where $d_{\overline{p}} = 1 - d_p$ and $d_{\overline{t}} = 1 - d_t$. We plot this
?? somewhere.

>>>>

?? Also there's heuristics. Figure out how to work this smoothly into the intro.

@@

Our experiments were performed on systems with Intel Xeon E5-4650 v2 (Q1'14) CPUs and 768GBytes RAM
(although this much RAM was not needed), running Scientific Linux release 6.7.   ?? Software
versions: Clasp 3.1.3, Gurobi 6.0.5, Glasgow, LAD version 2, VFLib. Software was compiled using GCC
4.9.

@@

By repeating the argument for locating the non-induced phase transition and additionally considering
non-edges, we get an expected number of solutions of \[ \langle Sol \rangle = t^{\underline{p}}
    \cdot {d_t}^{d_p \cdot \binom{p}{2}} \cdot {(1 - d_{t})}^{(1 - d_{p}) \cdot \binom{p}{2}}
\textnormal{.} \] We plot this
on the second row of \cref{figure:induced}---again, our prediction is accurate except for very
sparse or very dense patterns.
